### 2019-12-24 defesa/tex/chapter/definicoes.tex
wip

In this work, we are mostly interested in univariate polynomials defined over the complex numbers.
A function $p_n: \mathbb{C} \mapsto \mathbb{C}$ is a $n$-degree polynomial if it can be written as
\begin{equation}\label{eq:poly}
p_n(z) = \sum_{k=0}^{n} a_k z^k,
\end{equation}
with $a_0, \dots, a_n \in \mathbb{C}$.
The famous Abel-Ruffini Theorem (a proof can be seen in \citeonline{skopenkov2015}) states that for polynomials of degree higher than four, there is no closed formula\footnote{A finite number of $+, -, \times, \div, \sqrt{}$.} to determine their roots. Fortunately, a numerical approach exists for higher-degree polynomials which in practice works really well.

 In \citeonline[p.~195]{horn} a theorem is presented which says that for every univariate polynomial, there exists a companion matrix, such that its eigenvalues are the zeros of that polynomial. For example, the companion matrix of a degree-$5$ polynomial written as \autoref{eq:poly} is given by
 \begin{equation}
 \left[\begin{array}{ccccc}
 0 & 1 & 0 & 0 & 0\\
 0 & 0 & 1 & 0 & 0\\
 0 & 0 & 0 & 1 & 0\\
 0 & 0 & 0 & 0 & 1\\
 -\dfrac{a_0}{a_5} & -\dfrac{a_1}{a_5} & -\dfrac{a_2}{a_5} & -\dfrac{a_3}{a_5} & -\dfrac{a_4}{a_5}
 \end{array}\right].
 \end{equation}

>>>>

In this work, we are mostly interested in univariate polynomials defined over the complex numbers.
A function $p_n: \mathbb{C} \mapsto \mathbb{C}$ is a $n$-degree polynomial if it can be written as
\begin{equation}\label{eq:poly}
p_n(z) = \sum_{k=0}^{n} a_k z^k,
\end{equation}
with $a_0, \dots, a_n \in \mathbb{C}$. In this work, when a polynomial is written in the form of \autoref{eq:poly} we say that it is in the power form or in the monomial form, we have these terms for it because we also use a different base to represent polynomials which as a result .

The famous Abel-Ruffini Theorem (a proof can be seen in \citeonline{skopenkov2015}) states that for polynomials of degree higher than four, there is no closed formula\footnote{A finite number of $+, -, \times, \div, \sqrt{}$.} to determine their roots. Fortunately, a numerical approach exists for higher-degree polynomials which in practice works really well.

 In \citeonline[p.~195]{horn} a theorem is presented which says that for every univariate polynomial of degree $n$, there exists a companion matrix which is a $n\times n$ matrix, such that its eigenvalues are the zeros of that polynomial. For example, the companion matrix of a degree-$5$ polynomial written as \autoref{eq:poly} is given by
 \begin{equation}
 \left[\begin{array}{ccccc}
 0 & 1 & 0 & 0 & 0\\
 0 & 0 & 1 & 0 & 0\\
 0 & 0 & 0 & 1 & 0\\
 0 & 0 & 0 & 0 & 1\\
 -\dfrac{a_0}{a_5} & -\dfrac{a_1}{a_5} & -\dfrac{a_2}{a_5} & -\dfrac{a_3}{a_5} & -\dfrac{a_4}{a_5}
 \end{array}\right].
 \end{equation}
